Contextual Combinatorial Cascading Bandits

### 2015-11-23 contextual combinatorial cascading bandits.tex
update and rearrange structure
update second half part of 'Problem Formulation' section

At the end of time $t$, the agent observes $\bO_t, \bw_t(\ba_k^t), 1\leq k\leq\bO_t$ and receives the reward
\begin{align*}
\br_t &= \min_{1 \leq k \leq \abs{\bA_t}} [\gamma_k (1 - \bw_t(\ba_k^t)) +\gamma_0 \bw_t(\ba_k^t)] \\
&= \bigwedge_{k=1}^{\abs{A_t}} [\gamma_k (1 - \bw_t(\ba_k^t)) +\gamma_0 \bw_t(\ba_k^t)],
\end{align*}
where we use the notation that $\bigwedge_{1\leq i\leq n}a_i = \min_{1\leq i\leq n}a_i$. Note that every time $t$, we have observed.

If we define a function $f$ on $A=(a_1,...,a_{\abs{A}}) \in \cS, w=(w(1),...,w(L))$ by
\begin{align*}
f : \cS \times [0,1]^E \to [0,1]&~\\
f(A,w;\gamma_1,...,\gamma_K,\gamma_0) =& \sum_{k=1}^{\abs{A}}\gamma_k (\prod_{i=1}^{k-1}w(a_i))(1 - w(a_k)) \\
\qquad \qquad &~+ \gamma_0 \prod_{i=1}^{\abs{A}}w(a_i),
\end{align*}
then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t]=f(\bA_t,\theta_*^{\top}X_t)$ where $X_t=(X_{t,1} \cdots X_{t,L})\in\RR^{d\times L}$. Let 
$$
A_t^* = \argmax_{A\in \cS} f(A,\theta_*^{\top}X_t).
$$ 
The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
R(T) = \EE[\sum_{t=1}^T f(A_t^*, \theta_*^{\top}X_t) - f(\bA_t, \theta_*^{\top}X_t)].
$$
In the rest of this paper, we denote $\Delta_{t,\bA_t} = f(A_t^*, \theta_*^{\top}X_t) - f(\bA_t, \theta_*^{\top}X_t)$ and $R(T) = \EE[\sum_{t=1}^T \Delta_{t,\bA_t}]$.

@@

Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{X_s, \bA_s=(\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s): k \in[\bO_s], s\in[t] \}$ and $\EE_t[\cdot] = \EE[\cdot | \cH_t]$. By equation (\ref{eq:expectation}), we have $\EE[(\gamma_k'\bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k' X_{s,\ba_k^s})$. By ridge regression of data 
$$
\{(\gamma_k' X_{s,\ba_k^s}, \gamma_k'\bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]}
$$
where $\gamma_k' = \begin{cases}
\gamma_0, ~~k=1\\
\gamma_0-\gamma_k, ~~k\geq 2,
\end{cases}$
let $\hat{\theta}_t$ be the $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
\hat{\theta}_t = (X^{t,\top}X^{t} + \lambda I)^{-1} X^{t, \top} \bY^t
\end{equation}
where $X^t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k' X_{s,\ba_k^s}^{\top}$ and $\bY^t$ is the column vector whose elements are $\gamma_k' \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
\bV_t = X^{t,\top}X^{t} + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k'^2 X_{s,\ba_k^s}X_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix.

@@

Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all items in $E$. The UCB of item $a$ at time $t$ is defined as:
\begin{equation}
\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}X_{t,a} + \beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
\end{equation}
By theorem \ref{thm:theta_estimate}, it holds that
\begin{lemma}
\label{lem:estimateU}
For any $\delta > 0$, with high probability at least $1 - \delta$, for any $t>0$,
$$
0 \leq \bU_t(a) - \theta_*^{\top}X_{t,a} \leq 2\beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}
\begin{proof}
\begin{align*}
\abs{\hat{\theta}_{t-1}^{\top}X_{t,a} - \theta_*^{\top}X_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_*}_{\bV_{t-1}} \norm{X_{t,a}}_{\bV_{t-1}^{-1}} \\
&\leq \beta_{t}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}.
\end{align*}
\end{proof}

\begin{algorithm}
\caption{ConComCascade}
\label{alg:ConComCascade}
\begin{algorithmic}
\STATE {//Initialization}
\STATE {Parameters: $\delta > 0, \lambda >0, 1\geq \gamma_1\geq \cdots \geq \gamma_K > 0$}
\STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 0, \bV_0 = \lambda I$}
\STATE{}

\FORALL {$t=1,2,\ldots$}
\STATE {Obtain context $X_{t,a}$ for all $a\in E$}
\STATE{}

\STATE {//Compute UCBs}
\STATE {$\forall a\in E: $}
\STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}X_{t,a} + \beta_{t-1}(\delta)\norm{X_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
\STATE {}

@@

\STATE {//Update statistics}
\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 X_{t, \ba_k^t}X_{t, \ba_k^t}^{\top}$}
\STATE {$X^t \leftarrow ((X^{t-1})^\top, \gamma_1 X_{t, \ba_1^t},  ..., \gamma_{\bO_t} X_{t, \ba_{\bO_t}^t})^{\top}$}
\STATE {$Y^t \leftarrow ((Y^{t-1})^\top, \gamma_1 \bw(\ba_1^t),  ..., \gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t))^{\top}$}
\STATE {$\hat{\theta}_t \leftarrow ((X^{t})^\top X^{t} + \lambda I)^{-1} (X^{t})^\top \bY^t$}
\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\log(\det(\bV_{t})) + 2 \log(\frac{1}{\delta})} + \sqrt{\lambda}$}

@@

\begin{theorem}
For any $\delta > 0$, with probability at least $1 - \delta$, we have
\begin{equation}
R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT})
\end{equation}
\end{theorem}
\begin{proof}
With probability at least $1-\delta$,
\begin{equation}
\begin{split}
&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{\bA_t}] \\
&\leq \sum_{t=1}^{T} 4 \sqrt{\beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]}\\
&\leq 4\sqrt{\beta_T(\Delta)} \sum_{t=1}^{T} \sqrt{\bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}\\
&\leq 4\sqrt{\beta_T(\Delta)} \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
&\leq O(d^{3/4}\log(C_\gamma T)^{3/4}\sqrt{TK})
\end{split}
\end{equation}
\end{proof}

@@

\begin{lemma}
\label{lem:increasing} 
If $1 \leq \gamma_1 \leq ... \leq \gamma_K \leq \gamma_0 \leq 1$ and we have $w \leq w'$ as column vectors in $\RR^L$, then for any $A\in\cS$,
$$
f(A, w) \leq f(A, w').
$$
\end{lemma}
\begin{proof}
It suffices to prove that $\cA = [m]$ where $1 \leq m \leq K$. Because for $1 \leq k \leq m$,
\begin{align*}
&~~-\gamma_k + \sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j' + \gamma_0\prod_{j=k+1}^{m}w_j'\\
&\geq \gamma_k (-1 + \sum_{i=k+1}^m (1- w_i')\prod_{j=k+1}^{i-1}w_j' +  \prod_{j=k+1}^{m}w_j')\\
&=\gamma_k \cdot 0 = 0,
\end{align*}
then
\begin{align*}
&~~\gamma_k (1 - w_k) + w_k\sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j'\\
&\qquad \qquad + \gamma_0 w_k\prod_{j=k+1}^{m}w_j'\\
& \leq \gamma_k (1 - w_k') + w_k'\sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j'\\
&\qquad \qquad + \gamma_0 w_k'\prod_{j=k+1}^{m}w_j'.
\end{align*}
Therefore, 
\begin{align*}
& f(A; w_1,...,w_{k-1},w_k,w_{k+1}',...,w_m')\\
&=\sum_{i=1}^{k-1} \gamma_i(1 - w_i)\prod_{j=1}^{i-1}w_j + \prod_{j=1}^{k-1}w_j [\gamma_k (1 - w_k) \\
&\qquad + w_k\sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j' + \gamma_0 w_k\prod_{j=k+1}^{m}w_j'\\
&\leq \sum_{i=1}^{k-1} \gamma_i(1 - w_i)\prod_{j=1}^{i-1}w_j + \prod_{j=1}^{k-1}w_j [\gamma_k (1 - w_k') \\
&\qquad + w_k'\sum_{i=k+1}^m \gamma_i(1- w_i')\prod_{j=k+1}^{i-1}w_j' + \gamma_0 w_k'\prod_{j=k+1}^{m}w_j'\\
&=f(A; w_1,...,w_{k-1},w_{k}',w_{k+1}',...,w_m').
\end{align*}
Then we obtain the result.
\end{proof}

\begin{lemma}
\label{lem:estimateTech}
Suppose $0 \leq p_1,...,p_K \leq 1$ and $u_1,...,u_K \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}$. Then
\begin{align*}
&~~f(K, w) \leq f(K, p) + \sum_{k=1}^{K} \gamma_k' u_k
\end{align*}
\end{lemma}
\begin{proof}
We prove this by induction. It holds obviously for $K=1$.
\begin{align*}
&~~f(K+1, w)\\
&= f(K, w) -\gamma_0 \prod_{k=1}^{K} w_k + \gamma_{K+1} (1 - w_{K+1}) \prod_{k=1}^{K} w_k\\
&~~ + \gamma_0 \prod_{k=1}^{K+1} w_k\\
&= f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - w_{K+1}) \prod_{k=1}^{K} w_k\\
&\leq f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - w_{K+1}) \prod_{k=1}^{K} p_k\\
&\leq f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - p_{K+1} - u_{K+1}) \prod_{k=1}^{K} p_k\\
&\leq f(K, w) + (\gamma_{K+1} - \gamma_0) (1 - p_{K+1}) \prod_{k=1}^{K} p_k\\
&~~ + (\gamma_0 - \gamma_{K+1}) u_{K+1}\\
&\leq f(K+1, p) + \sum_{k=1}^{K+1} \gamma_k' u_k
\end{align*}
\end{proof}

@@

\begin{lemma}
Suppose $A = (a_1, ..., a_{\abs{A}})$. Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then we have the following properties.
\begin{itemize}
\item[(1)] $f(A, w) \leq \gamma_0 p_A + \gamma_{\abs{A}}$;
\item[(2)] $f(B_{k+1}, w) \leq f(B_k, w)$;
\item[(3)] $p_{B_{k+1}} \leq p_{B_k}$;
\item[(4)] $f(B_k, w) \leq \gamma_0 p_{B_{k+1}} + \gamma_{k+1}$.
\end{itemize}	
\end{lemma}

\begin{proof}
It suffices to prove these properties when $A = [m]$.
\begin{itemize}
\item[(1)]
$f(A, w) \leq \gamma_m(1 - p_A w_m) + \gamma_0 p_A w_m \leq \gamma_m + \gamma_0 p_A$

\item[(2)]
\begin{align*}
&f(B_k, w) - f(B_{k+1}, w)\\
&=\gamma_0 w_1 \cdots w_k - \gamma_{k+1} w_1 \cdots w_k (1 - w_{k+1})\\
&~~ - \gamma_0 w_1 \cdots w_{k} w_{k+1}\\
&=(\gamma_0 - \gamma_{k+1}) w_1 \cdots w_k (1 - w_{k+1}) \geq 0.
\end{align*}

@@

\item[(4)]
$f(B_k, w) \leq \gamma_k (1 - p_{B_{k+1}}) + \gamma_0 p_{B_{k+1}}\leq \gamma_0 p_{B_{k+1}} + \gamma_{k}$
\end{itemize}
\end{proof}

\begin{proposition}
Suppose $A = (a_1, ..., a_{\abs{A}})$. Then there exists a prefix $B$ of $A$, such that 
$$
p_{B} \geq \frac{\frac{1}{2}f^* - \gamma_{B}}{\gamma_0}, \qquad \Delta_{B} \geq \frac{1}{2}\Delta_A.
$$ 
\end{proposition}
\begin{proof}
	Notice that $f^* \leq \gamma_0$. By above lemma, we have $[f(A,w), \gamma_0] \subset \bigcup [f(B_k,w), \gamma_0 p_{B_k} + \gamma_k]$.
\end{proof}

\begin{proposition}
Suppose $\gamma_K \leq \frac{1}{4} f_t^*$. With high probability $1-\delta$, 
$$
E[\Delta_{\bA_t}|\cH_t] \leq \frac{4}{f_t^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
\end{proposition}
\begin{proof}
By above proposition, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\bB_t} \geq \frac{1}{4}\frac{f_t^*}{\gamma_0}$ and $\Delta_{\bB_t} \geq \frac{1}{2}\Delta_A$. Then we have
$$
\EE[\Delta_{\bA_t} | \cH_{t-1}] \leq \frac{4}{f_t^*} \EE[\Delta_{\bB_t} \bOne\{\Delta_{\bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
$$
Using $f(\bA_t^*,\bU_t) \leq f(\bA_t,\bU_t) \leq f(\bB_t,\bU_t)$ and lemma \ref{lem:estimateU}, \ref{lem:increasing}, it holds that
$$
f(\bA_t^*, \theta_*^{\top}X_t) \leq f(\bB_t,\bU_t).
$$
Then by lemma \ref{lem:estimateTech}
$$
f(\bB_t,\bU_t) \leq f(\bB_t, \theta_*^{\top}X_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k'\beta_{t-1}(\delta)\norm{X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore,
$$
\Delta_{\bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\gamma_k'\beta_{t-1}(\delta)\norm{X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
\end{proof}

\begin{corollary}
With high probability $1-\delta$, 
$$
E[\Delta_{\bA_t}|\cH_t] \leq 4\sqrt{\beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]}.
$$
\end{corollary}

>>>>

At the end of time $t$, the agent observes $\bO_t, \bw_t(\ba_k^t), 1\leq k\leq\bO_t$ and receives the reward
\begin{align*}
\br_t &= \begin{cases}
\gamma_{\bO_t - 1}  &\text{if } \bw_t(\ba_{\bO_t}^t) = 0\\
1 &\text{if } \bw_t(\ba_{\bO_t}^t) = 1,
\end{cases}\\
&=\begin{cases}
\gamma_{k - 1}  &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq k-1, \bw_t(\ba_{k}^t) = 0, k\leq \abs{\bA_t}\\
1 &\text{if } \bw_t(\ba_{i}^t) = 1, i\leq \abs{\bA_t},
\end{cases}
\end{align*}
where we use the notation of $\gamma_0 = 0$.

Given partial reward parameters $0 \leq \gamma_1 \leq \ldots \leq \gamma_{K-1} \leq 1$, we introduce a function $f$ on $A=(a_1,...,a_{\abs{A}}) \in \cS, w=(w(1),...,w(L))$ by
\begin{align*}
&f : \cS \times [0,1]^E \to [0,1]\\
&f(A,w) = \sum_{k=2}^{\abs{A}}\gamma_{k-1} (\prod_{i=1}^{k-1}w(a_i))(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
\end{align*}
then we have $\br_t = f(\bA_t, \bw_t)$ and $\EE[\br_t]=f(\bA_t,\theta_*^{\top}x_t)$ where $x_t=(x_{t,1}, \cdots, x_{t,L}) \in \RR^{d \times L}$. Let 
\begin{align*}
A_t^* &= \argmax_{A\in \cS} f(A,\theta_*^{\top}x_t),\\
f_t^* &= f(A_t^*, \theta_*^{\top}x_t).
\end{align*}
The goal of our learning algorithm is to minimize the expected cumulative regret in $T$ steps
$$
R(T) = \EE[\sum_{t=1}^T \Delta_{t,\bA_t}].
$$
where $\Delta_{t,\bA_t} = f_t^* - f(\bA_t, \theta_*^{\top}x_t)$.

@@

Let $\cH_t$ denote all history at the end of time $t$; $\cH_t$ consists of $\{x_s, \bA_s=(\ba_{1}^s,...,\ba_{\abs{\bA_s}}^s), \bO_s, \bw_s(\ba_k^s), k \in[\bO_s], s\in[t] \}$ and $\EE_t[\cdot] = \EE[\cdot | \cH_t]$. Let
$$
\gamma_k' = 1 - \gamma_{k-1}, ~~~1 \leq k \leq K.
$$
By equation (\ref{eq:expectation}), we have 
$$
\EE[(\gamma_k'\bw_{s,\ba_k^s}) | \cH_{s-1}] = \theta_*^{\top} (\gamma_k' x_{s,\ba_k^s}).
$$
By ridge regression of data 
$$
\{(\gamma_k' X_{s,\ba_k^s}, \gamma_k'\bw_{s,\ba_k^s})\}_{k \in[\bO_s], s\in[t]}
$$
where
let $\hat{\theta}_t$ be the $l^2$-regularized least-squares estimate of $\theta_*$ with regularization parameter $\lambda > 0$:
\begin{equation}
\hat{\theta}_t = (\bX_t^{\top}\bX_t + \lambda I)^{-1} \bX_t^{\top} \bY_t
\end{equation}
where $\bX_t \in \RR^{(\sum_{s=1}^{t}\bO_s) \times d}$ is the matrix whose rows are $\gamma_k' x_{s,\ba_k^s}^{\top}$ and $\bY_t$ is the column vector whose elements are $\gamma_k' \bw_s(\ba_k^s)$, $k \in[\bO_s], s\in[t]$. Let
$$
\bV_t = \bX_t^{\top} \bX_t + \lambda I = \lambda I + \sum_{s=1}^{t} \sum_{k=1}^{\bO_s} \gamma_k'^2 x_{s,\ba_k^s}x_{s,\ba_k^s}^{\top}.
$$
Then $\bV_t \in \RR^{d \times d}$ is a positive invertible matrix.

@@

Our proposed algorithm, ConComCascade, is described in Algorithm \ref{alg:ConComCascade}. First, it computes the upper confidence bounds (UCBs) $\bU_t \in [0,1]^{E}$ on the expected weights of all items in $E$. The UCB of item $a$ at time $t$ is defined as:
\begin{equation}
\bU_t(a) = \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}.
\end{equation}
By theorem \ref{thm:theta_estimate}, it holds that
\begin{lemma}
\label{lem:estimateU}
For any $\delta > 0$, with high probability at least $1 - \delta$, for any $t>0$,
$$
0 \leq \bU_t(a) - \theta_*^{\top}x_{t,a} \leq 2\beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}
\begin{proof}
\begin{align*}
\abs{\hat{\theta}_{t-1}^{\top}x_{t,a} - \theta_*^{\top}x_{t,a}} &\leq \norm{\hat{\theta}_{t-1} - \theta_*}_{\bV_{t-1}} \norm{x_{t,a}}_{\bV_{t-1}^{-1}} \\
&\leq \beta_{t}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}.
\end{align*}
\end{proof}

\begin{algorithm}
\caption{ConComCascade}
\label{alg:ConComCascade}
\begin{algorithmic}[1]
\STATE {//Initialization}
\STATE {Parameters: $\delta > 0, \lambda >0, 0 = \gamma_0 \leq \gamma_1 \leq \cdots \leq \gamma_{K-1} \leq 1$}
\STATE {$\hat{\theta}_0 = 0, \beta_0(\delta) = 1, \bV_0 = \lambda I$}
\STATE{}

\FORALL {$t=1,2,\ldots$}
\STATE {Obtain context $x_{t,a}$ for all $a\in E$}
\STATE{}

\STATE {//Compute UCBs}
\STATE {$\forall a\in E: $}
\STATE {$\bU_t(a) \leftarrow \min\{\hat{\theta}_{t-1}^{\top}x_{t,a} + \beta_{t-1}(\delta)\norm{x_{t,a}}_{\bV_{t-1}^{-1}}, 1\}$}
\STATE {}

@@

\STATE {//Update statistics}
\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
\STATE {$\bX_t \leftarrow [\bX_{t-1}^\top; ~\gamma_1' x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t}' x_{t, \ba_{\bO_t}^t}^{\top}]$}
\STATE {$\bY_t \leftarrow [\bY_{t-1}^\top; ~\gamma_1' \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t}' \bw_t(\ba_{\bO_t}^t)^{\top}]$}
\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\log(\det(\bV_{t})) + 2 \log(\frac{1}{\delta})} + \sqrt{\lambda}$}

@@

\begin{theorem}
For any $\delta > 0$, with probability at least $1 - \delta$, we have
\begin{equation}
R(T) = O(\frac{d}{f^*}\log(C_\gamma T)\sqrt{KT})
\end{equation}
\end{theorem}
\begin{proof}
With probability at least $1-\delta$,
\begin{equation}
\begin{split}
&R_T =\sum_{t=1}^{T} \EE_{t}[\Delta_{t, \bA_t}] \\
&\leq \sum_{t=1}^{T} 4 \beta_{t-1}(\delta) \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k' X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}]\\
&\leq 4 \beta_T(\delta) \sum_{t=1}^{T} \bO_t \EE[\sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]\\
&\leq 4 \beta_T(\Delta) \sqrt{(\sum_{t=1}^{T} \bO_t) \EE[\sum_{t=1}^{T} \sum_{k=1}^{\bO_t}\norm{\gamma_k'^2 X_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2]}  \\
&\leq O(d\log(C_\gamma T)\sqrt{TK})
\end{split}
\end{equation}
\end{proof}

@@

\begin{lemma}
\label{lem:increasing} 
If $0= \gamma_0 \leq \gamma_1 \leq ... \leq \gamma_{K-1} \leq 1$ and we have $0 \leq w \leq w' \leq 1$ as column vectors in $\RR^L$, then for any $A\in\cS$,
$$
f(A, w) \leq f(A, w').
$$
\end{lemma}
\begin{proof}
It suffices to prove that $\cA = [m]$ where $1 \leq m \leq K$. Because for $1 \leq k \leq m$,
\begin{align*}
&~~-\gamma_{k-1} + \sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i') + \prod_{j=k+1}^{m}w_j'\\
&\geq \gamma_{k-1} (-1 + \sum_{i=k+1}^m (\prod_{j=k+1}^{i-1}w_j')(1- w_i') +  \prod_{j=k+1}^{m}w_j')\\
&=\gamma_{k-1} \cdot 0 = 0,
\end{align*}
then
\begin{align*}
&~~\gamma_{k-1} (1 - w_k) + w_k\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i')\\
&\qquad \qquad + w_k\prod_{j=k+1}^{m}w_j'\\
& \leq \gamma_{k-1} (1 - w_k') + w_k'\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i')\\
&\qquad \qquad + w_k'\prod_{j=k+1}^{m}w_j'.
\end{align*}
Therefore, 
\begin{align*}
& f(A; w_1,...,w_{k-1},w_k,w_{k+1}',...,w_m')\\
&=\sum_{i=2}^{k-1} \gamma_{i-1} (\prod_{j=1}^{i-1}w_j)(1 - w_i) + (\prod_{j=1}^{k-1}w_j) [\gamma_{k-1} (1 - w_k) \\
&\qquad + w_k\sum_{i=k+1}^m \gamma_{i-1}(\prod_{j=k+1}^{i-1}w_j')(1- w_i') + w_k\prod_{j=k+1}^{m}w_j']\\
&\leq \sum_{i=2}^{k-1} \gamma_{i-1} (\prod_{j=1}^{i-1}w_j) (1 - w_i) + (\prod_{j=1}^{k-1}w_j) [\gamma_{k-1} (1 - w_k') \\
&\qquad + w_k'\sum_{i=k+1}^m \gamma_{i-1} (\prod_{j=k+1}^{i-1}w_j')(1- w_i') + w_k'\prod_{j=k+1}^{m}w_j']\\
&=f(A; w_1,...,w_{k-1},w_{k}',w_{k+1}',...,w_m').
\end{align*}
Then we obtain the result.
\end{proof}

\begin{lemma}
\label{lem:estimateTech}
Suppose $0 \leq p_1,...,p_m \leq 1$ and $u_1,...,u_m \geq 0$. Let $w_i = \min\{p_i + u_i, 1\}, 1 \leq i \leq m$. Then
$$
f(A^{(m)}, w) \leq f(A^{(m)}, p) + \sum_{k=1}^{m} \gamma_k' u_k,
$$
where $A^{(m)} = (1,2,\ldots,m), w = (w_1, \ldots, w_m)$ and $p = (p_1, \ldots, p_m)$.
\end{lemma}
\begin{proof}
We prove this by induction. It holds obviously for $m=1$.
\begin{align*}
&~~f(m+1, w)\\
&= f(m, w) -\prod_{k=1}^{m} w_k + \gamma_{m}  (\prod_{k=1}^{K} w_k) (1 - w_{K+1})+ \prod_{k=1}^{K+1} w_k\\
&= f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} w_k) (1 - w_{m+1})\\
&\leq f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} p_k) (1 - w_{m+1})\\
&\leq f(m, w) + (\gamma_{m} - 1) (\prod_{k=1}^{m} p_k)  (1 - p_{m+1} - u_{m+1})\\
&\leq f(m, p) +  \sum_{k=1}^{m} \gamma_k' u_k + (\gamma_{m} - 1) (1 - p_{m+1}) \prod_{k=1}^{m} p_k\\
&~~ + (1 - \gamma_{m}) u_{m+1}\\
&\leq f(m+1, p) + \sum_{k=1}^{m+1} \gamma_k' u_k
\end{align*}
\end{proof}

@@

\begin{lemma}
Suppose $A = (a_1, ..., a_{\abs{A}})$. Let $B_k = (a_1, ..., a_k), k \leq \abs{A}$ be a prefix of $A$. Then we have the following properties.
\begin{itemize}
\item[(1)] $f(A, w) \leq p_A + \gamma_{\abs{A} - 1}$;
\item[(2)] $f(B_{k+1}, w) \leq f(B_k, w)$;
\item[(3)] $p_{B_{k+1}} \leq p_{B_k}$;
\item[(4)] $f(B_k, w) \leq p_{B_{k+1}} + \gamma_{k}$.
\end{itemize}	
\end{lemma}

\begin{proof}
It suffices to prove these properties when $A = A^{(m)}$ and $w = (w_1, \ldots, w_m)$.
\begin{itemize}
\item[(1)]
$f(A, w) \leq \gamma_{m-1}(1 - p_A w_m) + p_A w_m \leq \gamma_{m-1} + p_A$;

\item[(2)]
\begin{align*}
&f(B_k, w) - f(B_{k+1}, w)\\
&=\prod_{i=1}^{k}w_i - \gamma_{k} (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) - (\prod_{i=1}^{k}w_i) w_{k+1}\\
&=(1 - \gamma_{k}) (\prod_{i=1}^{k}w_i) (1 - w_{k+1}) \geq 0.
\end{align*}

@@

\item[(4)]
$$
f(B_k, w) \leq \gamma_{k-1} (1 - p_{B_{k+1}}) + p_{B_{k+1}}\leq p_{B_{k+1}} + \gamma_{k}
$$
\end{itemize}
\end{proof}

\begin{proposition}
Suppose $A = (a_1, ..., a_{\abs{A}})$. Then there exists a prefix $B$ of $A$, such that 
$$
p_{B} \geq \frac{1}{2}f^* - \gamma_{\abs{B}-1}, \qquad \Delta_{B} \geq \frac{1}{2}\Delta_A.
$$ 
\end{proposition}
\begin{proof}
	Notice that $f^* \leq 1$. By above lemma, we have $[f(A,w), 1] \subset \bigcup [f(B_k,w), p_{B_k} + \gamma_{k-1}]$.
\end{proof}

\begin{proposition}
Suppose $\gamma_{K-1} \leq \frac{1}{4} f^*$. With high probability $1-\delta$, 
$$
E[\Delta_{t, \bA_t}|\cH_t] \leq \frac{4}{f^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k' x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
\end{proposition}
\begin{proof}
By above proposition, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\bB_t} \geq \frac{1}{4}f_t^*$ and $\Delta_{\bB_t} \geq \frac{1}{2}\Delta_A$. Then we have
$$
\EE[\Delta_{t, \bA_t} | \cH_{t-1}] \leq \frac{4}{f_t^*} \EE[\Delta_{t, \bB_t} \bOne\{\Delta_{t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
$$
Using $f(\bA_t^*,\bU_t) \leq f(\bA_t,\bU_t) \leq f(\bB_t,\bU_t)$ and lemma \ref{lem:estimateU}, \ref{lem:increasing}, it holds that
$$
f(\bA_t^*, \theta_*^{\top}X_t) \leq f(\bB_t,\bU_t).
$$
Then by lemma \ref{lem:estimateTech}
$$
f(\bB_t,\bU_t) \leq f(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k'\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore,
$$
\Delta_{\bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k' x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
\end{proof}
